%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer 2} % Job title
{Illumina} % Organization
{Singapore} % Location
{Apr. 2022 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed new product features in a microservice architecture and actively refactored code, applying knowledge of ASP.NET 6 and EF Core 6.}
    \item {Investigated multiple security violations of OAuth 2.0 Authorization Flows and misuse of Id Token, Access Token \& Refresh Token in a microservice architecture. Collaborated with teammates to deep-dive and propose mitigations and changes required in the architecture and other services. Also identified several improvements made possible after the above rectifications have been made. Presented to multiple stakeholders including a Principal Engineer \& Associate Director. Details of one of the mitigations can be found on my \href{https://zhiyuan-amos.github.io/blog/2023-02-07-access-token-short-lived-authorization-microservice/}{blog post}.}
    \item {Re-evaluated use of Keycloak as the Authorization Server and compared with the alternative of OpenIddict \& ASP.NET Core Identity. Presented to multiple stakeholders including Staff+ Engineers involved in choosing Keycloak, and proposed the scope of work and timeline required for migration.}
    \item {Revamped the format for interviewing candidates to better assess their capabilities and interviewed interns \& candidates for full-time positions. During post-mortem, the interviewers involved agreed that the new format better identifies false positives.}
    \item {Mentored junior engineers by conducting code reviews and pairing with them for multiple tasks. Also inspired them to do better work, sometimes through hard conversations such as performance and behaviour related conversations.}
    \item {Wrote unit tests using xUnit \& Moq. Also, deep-dived into testing strategies and consolidated information and shared with the team, which can be found on my \href{https://zhiyuan-amos.github.io/blog/2023-02-07-test-principles/}{blog post}.}
    \item {Improved tooling \& development process. For example, piloted Docusaurus to make documentation more delightful to read compared to Confluence, piloted Vertical-Slice Architecture, reversed the decision to hand-write the OpenAPI specification to generate the stub code.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer 1} % Job title
{Illumina} % Organization
{Singapore} % Location
{Feb. 2021 - Apr. 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented new features, upgraded dependencies and fixed bugs for a brownfield project using AngularJS 1.3, ASP.NET 4.6.1, RabbitMQ, Quartz.NET, ServiceStack, NHibernate, PostgreSQL, PowerShell and WiX Toolset, with Continuous Integration using TeamCity and Artifactory.}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ST Engineering} % Organization
    {Singapore} % Location
    {Dec. 2018 - July. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed the codebase for a greenfield project based on Vertical Slice Architecture and developed new product features, applying knowledge of ASP.NET Core 2.1, EF Core 2.1, Mediatr, SignalR and SQL.}
        \item {Identified and implemented Concurrency Control using both Pessimistic \& Optimistic Locks, and Application Security measures such as authentication, authorisation and protection against CSRF and XSS attacks.}
        \item {Provided technical guidance for a team of 4 developers by performing code reviews and suggested improvements and best practices to follow, and guided 2 junior developers on using Design Patterns such as MVVM for a C\# desktop application and Algorithmic Thinking.}
        \item {Simplified inherited legacy Java code substantially, resulting in a net decrease of 4.7kLoC, while fixing bugs and implementing multiple new features.}
        \item {Eliminated manual execution of performance tests for a Java desktop application by writing an automated test script in Python, saving 45 minutes per test execution.}
        \item {Eliminated the need for a team of ~20 programmers to perform repetitive chores such as manual cleaning of multiple cache folders (\textasciitilde10 times a day) by initiating and writing a PowerShell script.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Housing \& Development Board (HDB)} % Organization
    {Singapore} % Location
    {May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gathered User Requirements from scratch and redesigned the key workflow (performed 60 - 80 times per day per inspector) of the existing mobile application, reducing the number of steps required from 8 to 3.}
        \item {Automated the monthly generation of inspection schedule, reducing time taken to generate the schedule from 1 day to 15 minutes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {National University of Singapore - Open Source Software (NUS - OSS)} % Organization
    {Singapore} % Location
    {May. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Made improvements to a \href{https://github.com/issues?utf8=\%E2\%9C\%93&q=repo\%3Ase-edu\%2Faddressbook-level4+involves\%3AZhiyuan-Amos}{Java desktop application} used by National University of Singapore to teach students on Software Engineering by providing a model example of a high quality codebase for students to follow.}
        \item {Mentored a student under the Google Summer of Code program and guided new contributors by discussing with them on how to improve on the existing code architecture and reviewing their code.}
        \item {Wrote missing unit, integration and system tests, increasing test coverage from 90\% to 92\%.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Tutor - Programming Methodology} % Affiliation/role
    {NUS} % Organization/group
    {Singapore} % Location
    {Aug. 2016 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Led a group of 12 students in discussions to familiarize with fundamental concepts of problem solving by computing and programming using C language.}
        \item {Achieved an Overall Effectiveness Score of 4.40, which is 0.23 higher than the faculty average in School of Computing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
