%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {A Social Service Organisation} % Institution
    {Enhancing Data Entry \& Data Query} % Project Title
    {Singapore} % Location
    {Jan. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Created a Progressive Web Application from scratch, where I independently learnt and applied knowledge of Azure Static Web App, Azure Cosmos DB, .NET 5, EF Core 3.1, Blazor Web Assembly w/ Telerik, OData and Fluent Validation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.openinnovation.sg/about}{Open Innovation Platform}} % Institution
    {Integrated Solution for Contactless Check-In/Out} % Project Title
    {Singapore} % Location
    {Jul. 2020 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Led a team of 2 Software Engineers to gather User Requirements, design UI and explore technologies such as Progressive Web Application, Optical Character Recognition and Facial Recognition.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NUS} % Institution
    {Information Security Capstone Project} % Project Title
    {Singapore} % Location
    {Aug. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Analyzed security requirements, designed and implemented a secure web application using Java, Spring, Hibernate \& MySQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NUS} % Institution
    {Software Engineering on Modern Application Platforms} % Project Title
    {Singapore} % Location
    {Mar. 2017 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed an \href{https://github.com/Zhiyuan-Amos/Train-to-Changi}{iOS game} using Swift and applying knowledge of MVC architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NUS} % Institution
    {Independent Software Development Project} % Project Title
    {Singapore} % Location
    {May. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed an \href{https://github.com/Zhiyuan-Amos/Wut-2-Do}{Android mobile application} using Java, PHP, SQL and Google Maps API.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
